\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{PS5 Zilles}
\author{Andrew Zilles}
\date{March 2024}

\begin{document}

\maketitle

\section{What about it interests you? Will it be useful to you at some point in the future? Did you use any online tutorials to help you parse the data? If so, which ones?
}
Honestly, the data I pulled isn't that interesting. But the process is. I couldn't think of a good idea of something that I want to use in my future research and instead of spending too much time trying to find something useful I settled and decided to do something easy. Will the data be useful? Not really, I don't know how I'd use it. But learning how to scrape and massage the data so it's usable is definitely something I'll use in the future. I didn't use any online tutorials but ChatGPT was definitely my friend when I was trying to combine the tables and make it somewhat pretty.

\section{Tell me about what you found in the data (if anything) that was interesting or useful to you. What packages did you use (if any)?
}
I explored the MLB data using the baseballr package. It took me a while to figure out what the functions and arguments were and how to use them. I haven't gotten into the weeds of live play by play data yet, but just pulled up a simple schedule. I saw something like this (https://www.tomshardware.com/news/raspberry-pi-baseball-scoreboard) a while ago and thought it would be cool to make but I'm sure I won't get around to it for a few years. The hardware side is definitely over my head but the software side seems more doable now.
\end{document}